Cooperative Decision Making for Communities of Autonomous Web Services

### 2013-12-15 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes
ehsan

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame3 introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%\section{Motivation}
\subsection{Motivation}
    \begin{frame}{Motivation}
    \begin{itemize}
        \item High reliance on web services, created high competition and great business opportunities for online service developers
        \item Community of web services
        \item Goals:
        \begin{itemize}
            \item \textbf{User satisfaction, Service quality, high availability and responsiveness}.
            \item \textbf{Web Service Discovery over Internet}.
        \end{itemize}
    \end{itemize}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        %\includegraphics[width=1.0 \columnwidth]{figures/figure7.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}
    \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Problems and Research Questions}

@@

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Stability}
    \begin{itemize}
        \item We all want to work together and get $v(N)$, but we all have different views about how to share the fruits of our work. We can use the values of other coalitions as arguments in favor of a distribution.
        \item A condition for a coalition to form:
            {\color{red}all} agents prefer to be in it. i.e., none of the participants wishes she were in a different coalition or by herself {\color{red} $\Rightarrow Stability$ }
        \item The {\color{red} core} is a stability concepts for which no agents prefer to deviate to form a different coalition.
        \item Is the coalition stable $\Leftrightarrow$ Is the core non-empty
    \end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Solution Concepts: Core}
    CTLC logic is an extension of CTL logic with modalities for reasoning about \textbf{commitments and their fulfillment}.
    \begin{definition} [Imputation]\label{dfn:imputationbig}
        An {\color{red}imputation} is a payoff distribution $x$ that is efficient and individually rational.
        \begin{itemize}
            \item $\sum_{i \in N} x(i) = v(N)$ (efficiency)
            \item for all $i \in N, x_i \geq v(\{i\})$ (individual rationality)
        \end{itemize}
    \end{definition}

    \begin{definition} [Group rationality]\label{dfn:grouprationality}
        $\forall C \subseteq N, \sum_{i \in N} x(i) \geq v(C)$
    \end{definition}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame} {Solution Concepts: Core}
    The core relates to the stability of the grand coalition: \\ No group of agents has any incentive to change coalition.
    \begin{definition}[$Core$ of a game $(N,v)$]\label{dfn:core}
        Let $(N,v)$ be a cooperative game, and assume they form the coalition $N$. The core of $(N,v)$ is the set:
        \vspace{0.1cm}
        \begin{center}
            $Core(N,v) = \{x \in R^n | x$ is a group rational imputation$\}$
        \end{center}
        Equivalently,
        \vspace{0.1cm}
        \begin{center}
            $Core(N,v) = \{x \in R^n | x(N) \leq v(N) \wedge x(C) \geq v(C) \forall C \subseteq N\}$
        \end{center}
    \end{definition}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame3 introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%\section{Motivation}
\subsection{Motivation}
    \begin{frame}{Motivation}
    \begin{itemize}
        \item High reliance on web services, created high competition and great business opportunities for online service developers
        \item Community of web services
        \item Goals:
        \begin{itemize}
            \item \textbf{User satisfaction, Service quality, high availability and responsiveness}.
            \item \textbf{Facilitate Web Service Discovery over Internet}.
        \end{itemize}
    \end{itemize}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=1.0 \columnwidth]{figures/wsinternet.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}
    \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Problems and Research Questions}

@@

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Stability}
    \begin{itemize}
        \item We all want to work together and get $v(N)$, but we all have different views about how to share the fruits of our work. We can use the values of other coalitions as arguments in favor of a distribution.
        \item A condition for a coalition to form:
            {\color{red}all} agents prefer to be in it. i.e., none of the participants wishes she were in a different coalition or by herself {\color{red} $\Rightarrow Stability$ }
        \item The {\color{red} core} is a stability concepts for which no agents prefer to deviate to form a different coalition.
        \item Is the coalition stable $\Leftrightarrow$ Is the core non-empty
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame} {Solution Concepts: Core}
    The core relates to the stability of the grand coalition: \\ No group of agents has any incentive to change coalition.
    \begin{definition}[$Core$ of a game $(N,v)$]\label{dfn:core}
        Let $(N,v)$ be a cooperative game, and assume they form the coalition $N$. The core of $(N,v)$ is the set:
        \vspace{0.1cm}
        \begin{center}
            $Core(N,v) = \{x \in R^n | x$ is a group rational imputation$\}$
        \end{center}
        Equivalently,
        \vspace{0.1cm}
        \begin{center}
            $Core(N,v) = \{x \in R^n | x(N) \leq v(N) \wedge x(C) \geq v(C) \forall C \subseteq N\}$
        \end{center}
    \end{definition}
